Simple Mediation Example

### 2017-06-13 mediation.Rmd
updated function to include relationship between x and m.

  # fill in estimates from functions
  total_effect <- te_mod$coefficients[2]
  cde <- cde_mod$coefficients[2]
  nie <- m_x_mod$coefficients[2]*cde_mod$coefficients[3]

  estimates <- cbind(total_effect, cde, nie)
  return(estimates)

@@

# estimates (empty matrix)
est <- matrix(NA, ncol=4, nrow=3) 
colnames(est) <- c("est", "median", "lower_95", "upper_95")

@@

>>>>

  # fill in estimates from functions
  total_effect <- te_mod$coefficients[2]
  cde <- cde_mod$coefficients[2]
  nie <- m_x_mod$coefficients[2]*cde_mod$coefficients[3]
  x_affect_on_m <- m_x_mod$coefficients[2]

  estimates <- cbind(total_effect, cde, x_affect_on_m, nie)
  return(estimates)

@@

# estimates (empty matrix)
est <- matrix(NA, ncol=4, nrow=4) 
colnames(est) <- c("est", "median", "lower_95", "upper_95")

@@

# fill m x relationship
est[4,1] <- "x_m_association"
est[4,2] <- round(exp(quantile(boot_mediation$x_affect_on_m, 0.5)),3)
est[4,3] <- round(exp(quantile(boot_mediation$x_affect_on_m, 0.025)),3)
est[4,4] <- round(exp(quantile(boot_mediation$x_affect_on_m, 0.975)),3)
